Reflections from reproductions

### 2024-10-11 pages/reflections.qmd
docs(results): add extra TODO statements to results pages

>>>>

<!-- TODO: Consider whether to make further attempts at managing to backdate R. Didn't manage before. E.g. `containerit` package. Although - is it necessary, if I succeeded without? Note, I always backdated the python environments. So, relatedly, TODO: Is it worth checking/trying with newest Python and seeing if they would work?</mark -->

<!-- TODO: Add reflections related specifically to the reproduction package and second reproduction test parts of the work (i.e. after the reproduction) -->

<!-- TODO: Once complete, carefully go over again and check everything is correct -->
